# Goal interpolate the data where values are missing.
#Load packages
```{r}
library(bigrquery)
library(dplyr)
#library(DBI)
library(data.table)
library(glue)


#Authenticate
bq_auth()

# Define your GCP project and dataset
project_id <- "ut-deq-highfreq-dev"
dataset_id <- "AO_HF_Testing"

bqQuery <- function(query){
  project_id <- "ut-deq-highfreq-dev"
  query_job <- bq_project_query(project_id, query)
  table <- bq_table_download(query_job)
  return(table)
}

query1 <- "SELECT * FROM `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_collection_intervals`"
collection_intervals <- bqQuery(query1)
# Only DateTime_Local > Date(2018,10,01) for Temperature and Dissolved Oxygen
# CREATE OR REPLACE TABLE `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_IR26_time_diff` AS
#  SELECT *,TIMESTAMP_DIFF(DateTime_Local,LAG(DateTime_Local) OVER (PARTITION BY Sample_ID, Measurement_Description ORDER BY DateTime_Local),MINUTE) AS Previous_Timestamp_Diff 
# FROM `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_IR26_QC` 

#Query to get summary statistics to target which Sample_IDs may need to be reviewed.
# CREATE OR REPLACE TABLE `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_IR26_time_diff` AS
# SELECT *,  Water_Measurement - LAG(Water_Measurement) OVER (PARTITION BY Sample_ID, Measurement_Description ORDER BY DateTime_Local) AS Water_Measurement_Diff
# FROM `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_IR26_time_diff`
# ORDER BY  Sample_ID, Measurement_Description, DateTime_Local

query <- "
   SELECT
    Sample_ID,
    HF_Location_ID,
    DateTime_Local,
    Water_Measurement,
    Measurement_Description,
    Water_Measurement_Diff
FROM
    `ut-deq-highfreq-dev.AO_HF_Testing.temp_DO_IR26_time_diff`
WHERE Water_Measurement_Diff IS NOT NULL
ORDER BY
    Sample_ID,
    HF_Location_ID,
    Measurement_Description;
"
water_meas_diff <- bqQuery(query)

```

#Interpolate Function
```{r}
library(dplyr)
library(lubridate)
library(zoo)
library(data.table)

water_meas_diff_int <- water_meas_diff
# Convert dataset to data.table for efficient filtering
setDT(water_meas_diff_int)
setDT(collection_intervals)

# Merge collection interval with QC data
water_meas_diff_int <- merge(water_meas_diff_int, collection_intervals, by = c("Sample_ID", "Measurement_Description"), all.x = TRUE)

library(dplyr)
library(lubridate)
library(zoo)
library(data.table)

# Convert datasets to data.table for efficient operations
setDT(water_meas_diff1)
setDT(collection_intervals)

# Merge collection interval information
water_meas_diff2 <- merge(water_meas_diff1, collection_intervals, by = c("Sample_ID", "Measurement_Description"), all.x = TRUE)

# Define interpolation function
interpolate_data <- function(data) {
  # Ensure data is sorted by time
  data <- data[order(DateTime_Local)]
  
  # Get expected collection interval for this Sample_ID & Measurement_Description
  interval <- unique(data$Mode_Time_Difference_Minutes)
  if (is.na(interval) | length(interval) == 0) return(data)  # Skip if no interval info

  # Generate a complete sequence of timestamps at the expected interval
  complete_dates <- data.table(DateTime_Local = seq(min(data$DateTime_Local, na.rm = TRUE),
                                                    max(data$DateTime_Local, na.rm = TRUE),
                                                    by = paste(interval, "mins")))
  
  # Merge the complete sequence with existing data to find missing timestamps
  merged_data <- merge(complete_dates, data, by = "DateTime_Local", all.x = TRUE)
  
  # Identify time gaps
  merged_data[, time_diff := as.numeric(difftime(lead(DateTime_Local), DateTime_Local, units = "mins"))]
  
  # Interpolate only where:
  # - The value is missing (`is.na(Water_Measurement)`)
  # - The gap is **≤ 30 minutes**
  # - The surrounding values are NOT flagged as outliers
  merged_data[, Water_Measurement_Interpolated := ifelse(
    is.na(Water_Measurement) & (time_diff <= 30) & !lag(is_outlier, default = FALSE) & !lead(is_outlier, default = FALSE),
    na.approx(Water_Measurement, na.rm = FALSE),
    Water_Measurement
  )]

  # Create a QC flag for interpolated values
  merged_data[, Interpolation_Flag := ifelse(is.na(Water_Measurement) & !is.na(Water_Measurement_Interpolated), "Interpolated", NA)]
  
  # Drop temporary columns
  merged_data[, time_diff := NULL]

  return(merged_data)
}

# Apply function to each (Sample_ID, Measurement_Description) group
interpolated_water_data <- water_meas_diff2[, interpolate_data(.SD), by = .(Sample_ID, Measurement_Description)]

# Convert back to data.frame if needed
interpolated_water_data <- as.data.frame(interpolated_water_data)

# Save for review
save(interpolated_water_data, file = "interpolated_water_data.RData")
load("interpolated_water_data.RData")
getwd()
review_interp <- interpolated_water_data%>%mutate(diff_int = ifelse(Water_Measurement_Interpolated!=Water_Measurement,1,0))%>%
  filter(diff_int==1)


```



```{r}

water_meas_diff1 <- water_meas_diff %>%
  mutate(winter = ifelse(month(DateTime_Local)%in%c(11,12,1,2),1,0))%>%
  group_by(Sample_ID, HF_Location_ID,winter, Measurement_Description) %>%
  mutate(mean_value = mean(Water_Measurement, na.rm = TRUE),
    std_dev = sd(Water_Measurement, na.rm = TRUE),
    z_score = (Water_Measurement_Diff - mean(Water_Measurement_Diff, na.rm = TRUE)) / sd(Water_Measurement_Diff, na.rm = TRUE),
        is_outlier = abs(z_score) > 7
  ) %>%
  ungroup()



outlier_3_4 <- water_meas_diff1%>%filter(abs(z_score)>3.5)

# Identify potential sensor errors with extreme z-scores
outlier_samples <- water_meas_diff %>%
  filter(abs(z_score) > 3)  # Common threshold for outliers

# Identify Sensor Anomolies
sensor_anomalies <- water_meas_diff %>%
  group_by(Sample_ID, HF_Location_ID, Measurement_Description) %>%
  summarise(
    avg_diff = mean(Water_Measurement_Diff, na.rm = TRUE),
    min_diff = min(Water_Measurement_Diff, na.rm = TRUE),
    max_diff = max(Water_Measurement_Diff, na.rm = TRUE),
    std_dev = sd(Water_Measurement_Diff, na.rm = TRUE)
  ) %>%
  mutate(
    threshold_high = avg_diff + (2 * std_dev),
    threshold_low = avg_diff - (2 * std_dev)
  ) %>%
  ungroup()

# Identify where values exceed normal ranges
water_meas_diff_anomol <- water_meas_diff %>%
  inner_join(sensor_anomalies, by = c("Sample_ID", "HF_Location_ID", "Measurement_Description")) %>%
  mutate(anomoly = ifelse(Water_Measurement_Diff > threshold_high | Water_Measurement_Diff < threshold_low,1,0))

outlier_qc_review <- read_csv("~/Documents/GitHub/highfreqQC/HF_interpolation/QC_Review_Sample30_493_outlier2_99_2025-03-06.csv")

outlier_qc_review1 <-outlier_qc_review%>%
  group_by(Measurement_Description,QC_Flag)%>%
  summarize(avg_z = mean(z_score),
            avg_diff = mean(Water_Measurement_Diff),
            avg_meas = mean(Water_Measurement),
            counts = n())

library(ggplot2)

plot = ggplot(outlier_qc_review, aes(x = Measurement_Description, y =z_score, fill = QC_Flag)) +
  geom_boxplot() +
  scale_fill_manual(values = c("Potentially Erroneous" = "red", "OK" = "blue")) +
  theme_minimal() +
  labs(title = "QC Review: Measurement Distributions", 
       x = "Measurement Type", 
       y = "Water Measurement", 
       fill = "QC Flag") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
plot

ggplot(outlier_qc_review, aes(x = z_score, fill = QC_Flag)) +
  geom_density(alpha = 0.5) +  # Transparency for overlapping densities
  facet_wrap(~Measurement_Description, scales = "free") +  # Separate plots per measurement
  scale_fill_manual(values = c("Potentially Erroneous" = "red", "OK" = "blue")) +
  theme_minimal() +
  labs(title = "Distribution of Measurements by QC Flag", 
       x = "Water Measurement", 
       y = "Density", 
       fill = "QC Flag")


```


#Shiny App to view outlier values 
```{r}
library(shiny)
library(plotly)
library(dplyr)
library(data.table)
library(lubridate)
library(DT)
library(data.table)
outlier_sample_ids <- water_meas_diff1 %>%
  group_by(Sample_ID, Measurement_Description) %>%
  summarise(has_outlier = any(is_outlier), .groups = "drop") %>%
  filter(has_outlier) %>%
  select(Sample_ID, Measurement_Description)

# Keep only rows where Sample_ID and Measurement_Description match the outlier list
sample_data <- water_meas_diff1 %>%
  inner_join(outlier_sample_ids, by = c("Sample_ID", "Measurement_Description"))


# Convert to data.table
setDT(sample_data)

# Set keys for fast filtering
setkey(sample_data, Sample_ID, Measurement_Description, DateTime_Local)

save(sample_data,file="/outlier_bg_app/outlier_sample_data.Rdata")

temp_sample_data <-sample_data%>%filter(Measurement_Description=="Water Temperature")
save(temp_sample_data,file="/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/outlier_temperature_data.Rdata")


#Create UID for samples
names(temp_sample_data)

```
# Filter for only data in the critical periods
```{r}
#Keep Sample IDs only when there is a is_outlier == TRUE and that outlier is in months of c(5,6,7,8,9)
crit_period_temp_sample_data<- temp_sample_data%>%
  mutate(month = month(DateTime_Local),
         c_p = ifelse(is_outlier==TRUE& month%in%c(6,7,8,9),1,0),
         )%>%
    group_by(Sample_ID)%>%
  mutate(keep = any(c_p))%>%
  filter(keep==TRUE)

critical_season_temp <- crit_period_temp_sample_data %>%
  select(-keep,-c_p,-month)

print(length(unique(crit_period_temp_sample_data$Sample_ID)))

save(critical_season_temp,file="/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/critical_season_temp.Rdata")
load("/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/critical_season_temp.Rdata")
```
#Pull weather data from NOAA
```{r}
library(wqTools)
noaa_sites <-read.csv("noaa_weather_UT_sites.csv")

noaa_sites1 <- noaa_sites%>%
  select(-source_url,-etl_timestamp)%>%
  rename(LatitudeMeasure = latitude,LongitudeMeasure = longitude)%>%
  assignAUs(.)%>%
  assignHUCs()

unique_temp_sites <- unique(critical_season_temp$HF_Location_ID)

# Define your GCP project and dataset
project_id <- "ut-deq-highfreq-dev"

bqQuery <- function(project,query){
  project_id <- project
  query_job <- bq_project_query(project_id, query)
  table <- bq_table_download(query_job)
  return(table)
}

query1 <- "SELECT * FROM `ut-deq-highfreq-dev.High_Frequency_Flat_Views.Flatview_Location_Sampling_Event`"

location_sampling_events <- bqQuery(project_id,query1)

startDate <- as.character(as.Date(min(critical_season_temp[critical_season_temp$Sample_ID==29,]$DateTime_Local)))
endDate <- as.character(as.Date(max(critical_season_temp[critical_season_temp$Sample_ID==29,]$DateTime_Local)))
str(startDate)
query2 <- glue("SELECT
  *
FROM
  `ut-gee-dwq-uir-dev`.`noaa_weather_data`.`noaa_weather`
WHERE
  element IN ('PRCP',
    'SNOW',
    'TMAX',
    'TMIN',
    'TAVG')
  AND id IN ('US1UTBE0002',
    'US1UTBE0005')
  AND date BETWEEN '{startDate}'
  AND '{endDate}';")

test_data <- bqQuery(project_id,query2)

print(query2)
library(tidyverse)
library(leaflet) 

temperature_sites <- location_sampling_events%>%
  filter(HF_Location_ID%in%unique_temp_sites,State=="UT") %>%
  select(-ToolTip,-Folder_Link,-wqDataLiveID,-County, -Raw_Data_Folder_Link,-BigQuery_Entered,-Sample_ID,-Year_Deployed,-Logger_ID,-Collecting_Org)%>%
  distinct(.)%>%
  separate(LatLong,c("LatitudeMeasure", "LongitudeMeasure"),sep=",")%>%
  rename(MonitoringLocationName =Logger_Location_Description,MonitoringLocationIdentifier = HF_Location_ID,MonitoringLocationTypeName=Water_Name)%>%
  mutate(LatitudeMeasure = as.numeric(LatitudeMeasure),
         LongitudeMeasure = as.numeric(LongitudeMeasure))%>%
  assignHUCs(.)%>%
  assignAUs()

noaa_sites2 <- noaa_sites1%>%filter(HUC8%in%temperature_sites$HUC8)

library(geosphere)

# Define the radius in meters (10 miles)
radius_m <- 10 * 1609.34  # 16093.4 meters

# For each NOAA site, calculate its distance to every temperature site,
# then keep the minimum distance.
noaa_sites2_filtered <- noaa_sites2 %>%
  rowwise() %>%
  mutate(
    min_distance = min(
      distHaversine(
        cbind(LongitudeMeasure, LatitudeMeasure),
        cbind(temperature_sites$LongitudeMeasure, temperature_sites$LatitudeMeasure)
      )
    )
  ) %>%
  ungroup() %>%
  filter(min_distance <= radius_m)

# View the filtered NOAA sites
print(noaa_sites2_filtered)

#****** Download the noaa data_summary
query <- "SELECT * FROM `ut-gee-dwq-uir-dev.noaa_weather_data.data_summary`"

noaa_data_summaries <-bqQuery("ut-gee-dwq-uir-dev",query)

au_poly_trimmed <-wqTools::au_poly%>%filter(ASSESS_ID%in%noaa_sites2_filtered$ASSESS_ID|ASSESS_ID%in%temperature_sites$ASSESS_ID)
huc8_trimmed <- wqTools::huc8_poly%>%filter(HUC8%in%noaa_sites2_filtered$HUC8|HUC8%in%temperature_sites$HUC8)
huc12_trimmed <- wqTools::huc12_poly%>%filter(HUC12%in%noaa_sites2_filtered$HUC12|HUC12%in%temperature_sites$HUC12)

map1 = leaflet() %>%
  addMapPane( "underlay_polygons", zIndex = 410)%>%
  addMapPane( "au_poly", zIndex = 415)%>%
  addMapPane( "markers", zIndex = 420)%>%
  addProviderTiles( "Esri.WorldTopoMap", 
      group = "Topo", options = providerTileOptions(updateWhenZooming = FALSE, 
        updateWhenIdle = TRUE))%>%
  addCircleMarkers( lat = temperature_sites$LatitudeMeasure, 
      lng = temperature_sites$LongitudeMeasure, group = "Sites", color = "blue", 
      opacity = 0.8, options = pathOptions(pane = "markers"), # layerId = temperature_sites$locationID,
      popup = paste0("Location ID: ", temperature_sites$MonitoringLocationIdentifier, 
        "<br> Name: ", temperature_sites$MonitoringLocationName, "<br> Type: ")
      )%>%
  addCircleMarkers( lat = noaa_sites2_filtered$LatitudeMeasure, 
      lng = noaa_sites2_filtered$LongitudeMeasure, group = "Sites", color = "red", 
      opacity = 0.8, options = pathOptions(pane = "markers"), # layerId = temperature_sites$locationID,
      popup = paste0("Location ID: ", noaa_sites2_filtered$id, 
        "<br> Elevation: ", noaa_sites2_filtered$elevation, "<br> Type: ")) %>%
  addPolygons(
    data = huc8_trimmed, group = "HUC8",
    fillOpacity = 0.1, weight = 2, color = "purple",
    options = pathOptions(pane = "underlay_polygons") ) %>%
  addPolygons(
    data = au_poly_trimmed,group = "Assessment Units",
    fillOpacity = 0.1,weight = 2,color = "orange",
    options = pathOptions(pane = "au_poly"),
    popup = ~paste("AU Name:", AU_NAME, "<br> AU ID:", ASSESS_ID) ) %>%
  addPolygons(
    data = huc12_trimmed, group = "HUC12",
    fillOpacity = 0.1, weight = 2, color = "brown",
    options = pathOptions(pane = "underlay_polygons") )%>%
  addLayersControl(
    baseGroups = c("Topo"),  # You can add other base maps if desired
    overlayGroups = c("Sites (Blue)", "Sites (Red)", "HUC8", "Assessment Units", "HUC12"),
    options = layersControlOptions(collapsed = TRUE)
  )

map1


save(noaa_data_summaries,huc12_trimmed,au_poly_trimmed,huc8_trimmed,noaa_sites2_filtered,temperature_sites,file="/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/outlier_map_objects.Rdata")

load("/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/outlier_map_objects.Rdata")

```




# 2) Define what data would warrant interpolation: Assess eventID data then identify intervals of when the data is collected. Check for gaps of data, interpolate where gap max=2
```{r}
library(zoo)
names(raw_data100)
df_subset <- raw_data100 %>%
  mutate(
    DateTime_Local = as.POSIXct(DateTime_Local, format="%m/%d/%Y %H:%M:%S", tz="America/Denver")  # Ensure format matches
  ) %>%
  arrange(Sample_ID, Measurement_Description, DateTime_Local) %>%  # Ensure chronological order
  group_by(Sample_ID,HF_Location_ID, Measurement_Description) %>%  # Interpolation per parameter
  mutate(
    Time_Diff = as.numeric(difftime(lead(DateTime_Local), DateTime_Local, units="mins"))  # Corrected
  )
 ,
    Interpolated_Value = ifelse(
      Time_Diff > 0 & Time_Diff <= (2 * 15),  # 15-min intervals, max gap = 2 intervals
      na.approx(ResultMeasureValue, na.rm=FALSE), 
      NA
    )
  ) %>%
  ungroup()


```

#Download USGS sites to then query USGS API to pull weather data and flow data to compare against HF temperature data
```{r}
#****** To make it flexible may need to build API call to get list of sites from USGS to keep it up to date.
query1 <- "SELECT * FROM `ut-deq-highfreq-dev.High_Frequency_Data_USGS.USGS_Instantaneous_Sites`"
usgs_sites <- bqQuery(query1)

#Step 1: When Sample_Index changes or when app starts, you will identify the USGS sites near (maybe a 10 mile buffer if any?) 
library(geosphere)
library(data.table)

# Convert to data.table for speed 
setDT(temperature_sites)
setDT(usgs_sites)

# Result container
nearby_usgs <- list()

# Distance threshold in meters (10 miles)
threshold_meters <- 16093.4

# Loop through each temperature site
for (i in seq_len(nrow(temperature_sites))) {
  temp_site <- temperature_sites[i]
  temp_coords <- c(temp_site$LongitudeMeasure, temp_site$LatitudeMeasure)

  # Calculate distances from current temp site to all USGS sites
  distances <- distHaversine(temp_coords, usgs_sites[, .(Long, Lat)])
  
  usgs_sites[, distance := distances]
  # Get nearby USGS sites
  nearby <- usgs_sites[distances <= threshold_meters]
  
  # Add temperature site ID for reference
  if (nrow(nearby) > 0) {
    nearby[, temp_site_id := temp_site$MonitoringLocationIdentifier]
    nearby_usgs[[length(nearby_usgs) + 1]] <- nearby
  }
}

# Combine into a single data.table
nearby_usgs_all <- rbindlist(nearby_usgs)


# Step 2: and make an API call to get the min and max dates for flow and air temperature data. These USGS sites with data available near period of record will be plotted on the map with the NOAA sites.
library(httr)
library(jsonlite)


nearby_usgs_param_list <- list()

for (site_i in nearby_usgs_all$site_no) {
site_info <- paste0("https://waterservices.usgs.gov/nwis/iv/?format=json&sites=", site_i, "&parameterCd=all")
response <- httr::GET(site_info)
json_txt <- httr::content(response, as = "text", encoding = "UTF-8")
data <- jsonlite::fromJSON(json_txt, flatten = TRUE)

# print(data$value$timeSeries$variable.variableDescription)
# print(data$value$timeSeries$variable.variableCode)
# print(data$value$timeSeries$variable.variableName)

param_dt <- data.table(site_no = site_i,
  variableCode = sapply(data$value$timeSeries$variable.variableCode, function(x) x$value),
  variableName = data$value$timeSeries$variable.variableName,
  variableDescription = data$value$timeSeries$variable.variableDescription
)
nearby_usgs_param_list[[length(nearby_usgs_param_list) + 1]] <- param_dt

}

# Combine into a single data.table
nearby_usgs_param_list_all <- rbindlist(nearby_usgs_param_list)

nearby_usgs_param_list_all1 <- nearby_usgs_param_list_all %>% filter(variableDescription%in%c("Discharge, cubic feet per second" ,"Temperature, water, degrees Celsius" , "Precipitation, total, inches","Temperature, air, degrees Fahrenheit"))%>%
  distinct()
str(nearby_usgs_param_list_all1)


nearby_usgs_all_2 <-nearby_usgs_all %>%filter(site_no%in%nearby_usgs_param_list_all1$site_no)

save(nearby_usgs_param_list_all1,nearby_usgs_all_2,file="/Users/alanochoa/Documents/GitHub/highfreqQC/HF_interpolation/outlier_bq_app/usgs_site_data.Rdata")
load("usgs_site_data.Rdata")
#-------------------------------------------------------------

download_USGS_data <- function(site_no,params,start,end) 
  {
site_no <- "10129300"
params <- c("00060")  # flow and water temp
start <- "2019-07-04"
end <- "2022-10-22"

url <- paste0(
  "https://waterservices.usgs.gov/nwis/iv/?sites=", site_no,
  "&parameterCd=", paste(params, collapse = ","),
  "&startDT=", start,
  "&endDT=", end,
  "&format=json"
)

res <- fromJSON(content(GET(url), "text"))

# Assuming `res` is your parsed JSON object (from fromJSON())
p_length <- length(res$value$timeSeries$variable$variableCode)

all_data <- list()  # Store individual tables

for (i in seq_len(p_length)) {
  print(i)
  ts_entry <- res$value$timeSeries$values[[i]]
  
  # Extract metadata
  variable_code <- res$value$timeSeries$variable$variableCode[[i]]$value
  variable_desc <- res$value$timeSeries$variable$variableDescription[i]
  site_id <- res$value$timeSeries$sourceInfo$siteCode[[1]]$value
  unit <- res$value$timeSeries$variable$unit$unitCode[i]
  
  # Extract values (dateTime and value columns)
  df <- as.data.table(ts_entry$value[[1]])  # Flatten
  if (nrow(df) > 0) {
    df[, variable_code := variable_code]
    df[, variable_desc := variable_desc]
    df[, site_id := site_id]
    df[, unit := unit]
    
    # Combine into the master list
    all_data[[i]] <- df
  }
}

# Combine all into one data.table
combined_data <- rbindlist(all_data, fill = TRUE)
# Ensure dateTime is POSIXct in UTC
combined_data[, dateTime := as.POSIXct(dateTime, format="%Y-%m-%dT%H:%M:%S", tz="UTC")]

# Convert to MST/MDT (Mountain Time, auto handles DST)
combined_data[, dateTime_local := with_tz(dateTime, tzone = "America/Denver")]
  combined_data[, datetime_30min := floor_date(dateTime_local, unit = "30 minutes")]

# Calculate average value per 30-minute window and variable
combined_avg <- combined_data[
  , .(mean_value = mean(as.numeric(value), na.rm = TRUE)),
  by = .(site_id,datetime_30min, variable_code, variable_desc, unit)
]
return(combined_data)
}

# Step 3: There are still too many USGS sites that don't have data for specifc site of interest period of record. Will need to manually download all combinations:
nearby_usgs_all_3 <- nearby_usgs_all_2%>%
  select(-HF_Location_ID,-MLID,-Site_Type,-State,-County,-USGS_HUC12,-function_batch,-Sample_ID)%>%
  rename(HF_Location_ID = temp_site_id)

# Create a summary tab for all the Sample_ID,HF_Location_ID,date_min,date_max
temperature_dates <- critical_season_temp%>%
  group_by(Sample_ID,HF_Location_ID)%>%
  summarize(min_date =min(DateTime_Local),
            max_date = max(DateTime_Local))

# merge nearby_usgs_all_3 with temperature_dates
nearby_usgs_all_4 <- merge(nearby_usgs_all_3,temperature_dates,by ="HF_Location_ID" )

```


# 3) After data has been interpolated, push back or update to original duplicated_test_table. Research best route: 

# R1) Remove working EventID from duplicated_test_table, and paste into temporary_backup_interpolated_table
# R2) Leave all data in and when you push and update the table it only updates the rows where the EventID is the same{also build check to get count of new amounts of data}

# R3) Are there any other possible routes that can be taken? 


# 4) If this was a dashboard where you iterate through each EventID, this maybe helpful to review. The features could include:
# a) Summary Table of EventIDs MinDate, MaxDate, List of Parameters for EventID, Record_Numbers, # b) User selects an event ID :below table or on side panel click there are buttons {Interpolate_all_params, Review_Interpolation } : 
# c) Summary of previous record count vs new record count {by param level - site, param, counts}
# d) Graph to display record values, {add filter by Parameter}, colorcode for interpolated values as red others as blue or similar. AND Add Previous, Next Record buttons to zoom into individual interpolated values.
# e) What kind of additional stats can we add to easily view /flag potentially eroneous interpolated values? For example if we were to interpolate at a min or max?



